Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-10-27 paper/main_RA-L_v1.tex
Changed A to script A

%Lastly, we wish to capture joint-space behaviors in our dynamical system.
We make two decisions by the choice of behavior error metric \eqref{eq:optim_error}. First, the metric implicitly suggests that behaviors are defined by expert motions of the behavior, and that fulfilling a behavior means moving similarly to the experts' motion. Second, the type of feature of the trajectory that is being minimized is important. If instead the error feature were joint position distance $\sum_i\left \| q_{d,i} - q_i \right \|$ where $q_d$ is a vector of demonstrated positions, then executing a "behavior" would imply mimicking position, but not velocity. Alternatively, if the error feature were joint velocity direction $\sum_i \left | \frac{\dot{q}_{d,i}}{\left \| \dot{q}_{d,i} \right \|} - \frac{\dot{q}_i}{\left \| \dot{q}_i \right \|} \right |$ mimicking a "behavior" would involve following the motion profile, but not the motion's speed (so for example a slap and a push would exhibit the same behavior). By choosing the combined direction and magnitude of the joint velocity as the error, we are choosing to mimic the magnitude and direction of the motion, which \cite{gielniak2010stylized} suggests is visually most similar to the human definition of "joint motion style".
\section{Augmented \textbf{J}oint-Space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem} \label{Sec:DS}
\label{sec:proposed_system}
\textcolor{red}{Change semi-definite to definite everywhere\\Change overall $A(q)$ to $\mathcal{A}(q)$\\ Introduce 'behavior synergies' here\\}
We propose the following augmented Joint-space Task-oriented Dynamical System (JTDS) to achieve the two criteria presented in \ref{eq:Lyp} and \ref{eq:optim_error}.
\begin{equation}
\label{eq:ds}
\dot{q} = f(q) = -A(q)J^T(q)P(H(q) - x^*)
\end{equation}
where $P\in \mathbb{R}^{d\times d}$, and $A(q)\in \mathbb{R}^{m\times m}$ is constructed using the Linear Parameter Varying system paradigm \cite{emedi2016fixed,7439839}, where the overall $A(q)$ is a changing linear combination of constant  matrices, each of which encodes a local joint-space synergy. 
\begin{equation}
\label{eq:A_def}
A(q) = \sum_{k=1}^{K}\theta_k(q)A_k 
\end{equation}
where $A_k\in \mathbb{R}^{m\times m} $ are the different synergies and $\theta_k(q)\in \mathbb{R}^{1}~\forall k\in\{1,\dots,K\} $ are the scheduling parameters\footnote{The scheduling parameters can be a function of time $t$, the states of the
system $q $ or external signals $d(t)$, i.e. $\theta_k (t, q(t), d(t))$. In this paper, we only consider it as a function of the states of the system. It is noteworthy that the presented stability proof can easily be extended for $\theta_k (t, q(t), d(t))$.} modulating each local synergy through time as well as space. Based on \eqref{eq:ds}, one can utilize different synergies in different regions, and compose them to create a more complex multi-behavior motion.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{Pic/A_comparison_positions.pdf}
\caption{Three example 3-DOF motions (A, B, C), each with a different constant joint augmentation matrix $A$ (emphasizing the hip, knee, and ankle respectively), A: $A(q)=diag(5,1,1) $, B: $A(q)=diag(1,5,1)$, and C: $A(q)=diag(1,1,5)$. On the left, the task-space traces of each motion. On the right, the time-scaled joint positions of each joint. Each motion tends to use its ``primary" joint most and uses the other available joints to compensate for what the primary joint cannot do.}
\label{fig:A_example}
\vspace{-15pt}
\end{figure}

Before proving that the proposed dynamical system satisfies all of the criteria, let us establish an intuitive understanding of the components of the system. While it may seem daunting at first, each of the elements has a straightforward explanation. One can intuitively understand the control law as follows: $(H(q) - x^*)$ denotes the position error w.r.t. the task target (warped according to P), and by multiplying that error by the transposed Jacobian $J^T(q)$, the error is projected into joint space (similar to Jacobian transpose control \cite{wolovich1984computational,sciavicco1988solution}). The positive semi-definite matrix $A(q)$ warps the resulting joint-space velocity; Fig. \ref{fig:A_example} illustrates the effects of  $A(q)$ on the generated motion. Thus the controller can be thought of as a proportional controller in joint space. Lastly, we refer to the $P$ matrix as the \begin{bf} task augmentation matrix \end{bf}(because it augments the task error, and thus the direction of motion) and $A(q)$ as the \begin{bf} joint augmentation matrix \end{bf} (because it augments the outputted joint velocities).
%When using each of these matrices, the controller will augment the joint velocities to favor using one joint more than the others (in $A_1$ the hip, in $A_2$ the knee, and in $A_3$ the ankle). This ''augmentation" is simply a matrix multiplication ($A\dot{q}_{raw}$). The components of the outputted velocity are linear combinations of the ''raw" un-augmented joint velocities, where the entries in $A$ define the precise ratios. We can see the joint positions resulting from our experiment over time on the right side of Fig. \ref{fig:A_example}. Each motion tends to use its ``primary" joint most (the joint where the velocity is heavily scaled up) and uses the other available joints to compensate for what the primary joint cannot do. For example, Motion 1 starts out using mostly the hip, but once moving the hip no longer brings the system closer to the goal, the system uses the other joints to fold inwards and reach the goal. Ultimately, all three controllers converge on their target, but each has a different path through joint space depending on which joints we choose to emphasize in the behavior matrix $A$. The off-diagonal terms of $A$ have a more nuanced contribution; e.g. $A_{1,2}$ defines the amount that elbow velocity should be converted into hip velocity.

@@

%By learning a position-dependent joint augmentation matrix $A(q)$, we are able to execute the joint behaviors discussed earlier by augment the relative velocities of our joints. \eqref{eq:A_def} constructs our overall $A(q)$ as a linear combination of $A_k~\forall k\in\{1,\dots,K\}$ (each weighted by $\theta_k(q)$), where one can enforce different local joint behaviors in different regions, and compose them to create a more complex multi-behavior motion. In this paper the joint behavior matrix $A(q)$ is determined using only the joint position $q$, though one could potentially use other information such as joint velocity $\dot{q}$, environment force or target task position $x^*$.\\

@@

The behavior of the JT-DS algorithm can be best understood through the lens of synergy control \cite{petrivc2013muscle}. In robotic synergy control, a robot's movements can be decomposed into a small number of synergies: principal components of the actuation-space that are sufficient to accurately recreate the desired robotic behaviors. In our case, the synergies are represented by $A_1, A_2, \dots, A_k$, and $A(q)$ represents the resulting motion constructed from a superposition of different synergies (through \eqref{eq:ds}).

@@

\subsection{Estimating the Synergy Matrices}
Given the parameters of $\theta_k'(\phi(q))$ $\forall k \in \{k=1,\dots,K\}$, from \eqref{eq:A_def} one can construct $A(q)$ as a linear combination of local $A_k$ matrices weighted by their scheduling parameters $\theta_k'(\phi(q))$ as follows: 
\begin{equation}
\label{eq:A}
A(q) = \frac{\sum_{k=1}^K A_k \pi_k\mathcal{N}(\phi(q); \mu_k, \Sigma_k)}{\sum_{k=1}^K \pi_k\mathcal{N} (\phi(q); \mu_k, \Sigma_k)}.
\end{equation} 
Notice the resemblance of \eqref{eq:A} to the Nadaraya-Watson kernel estimator \cite{nadaraya1964regress,watson1964regress}\footnote{The Nadaraya-Watson kernel estimator is used to estimate an unknown regressive function $m(x) = \mathbb{E}\{Y|X\}$, which takes the general form of $\widehat{m}(x) = \frac{\sum_{i=1}^n y_i \mathcal{K}(x,x_i)}{\sum_{i=1}^n \mathcal{K}(x,x_i)}$ where $\mathcal{K}(x,x_i)$ is a kernel function denoting the distance or similarity of $x_i$ to the given location $x$. \cite{nadaraya1964regress,watson1964regress}} with a Gaussian pdf as its kernel function. Hence \eqref{eq:A} can be considered a type of kernel estimator, with the key distinction that the weighting functions $\theta_k'(\phi(q))$ are not determined by individual points (as in the original Nadaraya-Watson kernel estimator) but by the components of a GMM, similar to the weighting functions derived in Gaussian Mixture Regression (GMR) \cite{sung2004gmr}.

@@

One of the most important points when validating a learning from demonstration method is to evaluate the system's behavior away from demonstrations. When the current joint configuration is far from any of the local synergy regions, computing the scheduling parameters $\theta_k(\cdot)$ becomes numerically infeasible (all the Gaussians in \eqref{eq:A} $\rightarrow 0$), and so $\sum\limits_{k=1}^{K}\frac{A_k}{K}$ is used to move the robot, which is still guaranteed to move towards the target. Moreover, in overlapping local regions where multiple $A_k$'s might be in conflict, the presented system compromises between them while still stably moving to the target. The reason for this is that rather than ``determining" the velocity of the system, our $A$ matrix only warps it. This means that adding multiple ``conflicting" synergies together amounts to nothing more than repeatedly warping the velocity, and still maintains the original stability property.

@@

JTDS can be expanded to incorporate joint limits of the form $q^i_{max} > q^i > q^i_{min}$. Previous work proposed adding discontinuous limits to JT control \cite{sciavicco1988solution}, and we additionally propose a continuous modification as follows: \textcolor{red}{Remove this part? Should we not talk about continuous joint limiting?} Replace the combined synergy matrix $A(q)$ with a joint-limited joint-behavior matrix $\mathcal{A} = S(q)A(q)S^T(q)$, where $S(q)$ is a bounded positive semidefinite diagonal matrix such that  
\begin{equation}
\label{eq:last_criteria}
\begin{cases}
\begin{split}
& s^{i}(q^i_{max}) = 0&&&\\
& s^{i}(q^i_{min})= 0&&&
\end{split}
\forall i\in 1,\dots,m
\end{cases}
\end{equation}
$\mathbb{A}$ is also positive semidefinite, so the system is still provably stable w.r.t. the attractor. The structure of $S$ enforces kinematic joint limits because as a joint nears one of its limits, its magnitude decreases such that it will never actually collide with the limit. One way of constructing $S$ is to use the following function:
\begin{equation}
s^{i}(q) =
1 - \left ( 2\frac{q^i - q^i_{min}}{q^i_{max} - q^i_{min}} - 1 \right ) ^{4}  ~\forall i\in 1,\dots,m\\
\end{equation}
The algorithm can similarly be expanded to accommodate joint velocity limits by scaling the controller's velocity down such that the highest-velocity component is still within the velocity limits. Specifically, given some set of velocity constraints for each joint $i$ s.t. $\dot{q}_i < \dot{q}_{i, max}$, we can design a new joint augmentation matrix $\mathcal{A}' = r \mathcal{A}$ where $r = \min \left ( 1, \max_i \left ( \frac{\dot{q}_{i, max}}{\dot{q}_i} \right ) \right )$. This velocity scalar would slow down the joint trajectory when the robot dynamics could not execute them, but would not change the position profile of the joint motion, preserving a major aspect of the joint behavior.

@@

\section{Proving Stability of the Dynamical System}
\label{appendix:stability}
We wish to prove Proposition \ref{prop:stability}, that is, that JT-DS \eqref{eq:ds} (reproduced below)
\begin{equation*}
\dot{q} = f(q) = -A(q)J^T(q)P(H(q) - x^*)
\end{equation*}
accomplishes criterion (I), where $A$ is positive semi-definite, and $P$ is positive definite.
\newtheorem{theorem}{Theorem}[section]
\begin{theorem}[Proof of Lyapunov Stability]
JT-DS \eqref{eq:ds} is stable in the sense of Lyapunov with respect to the Lyapunov candidate
\[ V(q) = \frac{1}{2}(H(q) - x^*)^TP(H(q) - x^*) \]
That is, 
\begin{equation}
\begin{aligned}
& 0 \prec V(q)    &
V(q^*) = 0 & \quad \forall q \neq q^*\\
%    \[\dot{V}(q) = \frac{dV}{dq}\frac{dq}{dt}(q) \preceq 0 \quad \forall q \in Q\]
\end{aligned}
\end{equation}
where $q^*$ is any joint configuration such that $H(q^*) = x^*$.
\end{theorem}
The first two statements are trivially true because $P$ is positive definite and the rest of $V$ is a square that is only $0$ when $H(q) = x^*$. To prove the last statement, we find $\frac{dV}{dt}$:
\begin{equation}
\begin{aligned}
\frac{dV(q)}{dt} &= (H(q) - x^*)^TPJ(q)\dot{q}\\
&= -(H(q) - x^*)^TPJ(q)A(q)J^T(q)P(H(q) - x^*)\\
&= -(H(q) - x^*)^TPJ(q)\sum_{k=1}^{K}\underbrace{\theta_k(q)}_{0\leq}\underbrace{A_k}_{0\preceq}\\&~~~~~~ \cdot J^T(q)P(H(q) - x^*) \leq 0
\end{aligned}
\end{equation}
By observation, each and every term in the final expression is multiplied by its transpose (creating a square) except for $A$, which is positive semi-definite. This means that the expression is guaranteed to be negative semi-definite. Therefore, JT-DS \eqref{eq:ds} is globally Lyapunov stable; i.e. $ \| H(q)-x^*\| $ and $ \dot{q} $ are bounded.

>>>>

%Lastly, we wish to capture joint-space behaviors in our dynamical system.
We make two decisions by the choice of behavior error metric \eqref{eq:optim_error}. First, the metric implicitly suggests that behaviors are defined by expert motions of the behavior, and that fulfilling a behavior means moving similarly to the experts' motion. Second, the type of feature of the trajectory that is being minimized is important. If instead the error feature were joint position distance $\sum_i\left \| q_{d,i} - q_i \right \|$ where $q_d$ is a vector of demonstrated positions, then executing a "behavior" would imply mimicking position, but not velocity. Alternatively, if the error feature were joint velocity direction $\sum_i \left | \frac{\dot{q}_{d,i}}{\left \| \dot{q}_{d,i} \right \|} - \frac{\dot{q}_i}{\left \| \dot{q}_i \right \|} \right |$ mimicking a "behavior" would involve following the motion profile, but not the motion's speed (so for example a slap and a push would exhibit the same behavior). By choosing the combined direction and magnitude of the joint velocity as the error, we are choosing to mimic the magnitude and direction of the motion, which \cite{gielniak2010stylized} suggests is visually most similar to the human definition of "joint motion style".
\section{Augmented \textbf{J}oint-Space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem} \label{Sec:DS}
\label{sec:proposed_system}
\textcolor{red}{Change semi-definite to definite everywhere\\ Introduce 'behavior synergies' here\\}
We propose the following augmented Joint-space Task-oriented Dynamical System (JTDS) to achieve the two criteria presented in \ref{eq:Lyp} and \ref{eq:optim_error}.
\begin{equation}
\label{eq:ds}
\dot{q} = f(q) = -\mathcal{A}(q)J^T(q)P(H(q) - x^*)
\end{equation}
where $P\in \mathbb{R}^{d\times d}$, and $\mathcal{A}(q)\in \mathbb{R}^{m\times m}$ is constructed using the Linear Parameter Varying system paradigm \cite{emedi2016fixed,7439839}, where the overall $\mathcal{A}(q)$ is a changing linear combination of constant  matrices, each of which encodes a local joint-space synergy. 
\begin{equation}
\label{eq:A_def}
\mathcal{A}(q) = \sum_{k=1}^{K}\theta_k(q)A_k 
\end{equation}
where $A_k\in \mathbb{R}^{m\times m} $ are the different synergies and $\theta_k(q)\in \mathbb{R}^{1}~\forall k\in\{1,\dots,K\} $ are the scheduling parameters\footnote{The scheduling parameters can be a function of time $t$, the states of the
system $q $ or external signals $d(t)$, i.e. $\theta_k (t, q(t), d(t))$. In this paper, we only consider it as a function of the states of the system. It is noteworthy that the presented stability proof can easily be extended for $\theta_k (t, q(t), d(t))$.} modulating each local synergy through time as well as space. Based on \eqref{eq:ds}, one can utilize different synergies in different regions, and compose them to create a more complex multi-behavior motion.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{Pic/A_comparison_positions.pdf}
\caption{Three example 3-DOF motions (A, B, C), each with a different constant joint augmentation matrix $\mathcal{A}(q)$ (emphasizing the hip, knee, and ankle respectively), A: $\mathcal{A}(q)=diag(5,1,1) $, B: $\mathcal{A}(q)=diag(1,5,1)$, and C: $\mathcal{A}(q)=diag(1,1,5)$. On the left, the task-space traces of each motion. On the right, the time-scaled joint positions of each joint. Each motion tends to use its ``primary" joint most and uses the other available joints to compensate for what the primary joint cannot do.}
\label{fig:A_example}
\vspace{-15pt}
\end{figure}

Before proving that the proposed dynamical system satisfies all of the criteria, let us establish an intuitive understanding of the components of the system. While it may seem daunting at first, each of the elements has a straightforward explanation. One can intuitively understand the control law as follows: $(H(q) - x^*)$ denotes the position error w.r.t. the task target (warped according to P), and by multiplying that error by the transposed Jacobian $J^T(q)$, the error is projected into joint space (similar to Jacobian transpose control \cite{wolovich1984computational,sciavicco1988solution}). The positive semi-definite matrix $\mathcal{A}(q)$ warps the resulting joint-space velocity; Fig. \ref{fig:A_example} illustrates the effects of  $\mathcal{A}(q)$ on the generated motion. Thus the controller can be thought of as a proportional controller in joint space. Lastly, we refer to the $P$ matrix as the \begin{bf} task augmentation matrix \end{bf}(because it augments the task error, and thus the direction of motion) and $\mathcal{A}(q)$ as the \begin{bf} joint augmentation matrix \end{bf} (because it augments the outputted joint velocities).
%When using each of these matrices, the controller will augment the joint velocities to favor using one joint more than the others (in $A_1$ the hip, in $A_2$ the knee, and in $A_3$ the ankle). This ''augmentation" is simply a matrix multiplication ($A\dot{q}_{raw}$). The components of the outputted velocity are linear combinations of the ''raw" un-augmented joint velocities, where the entries in $A$ define the precise ratios. We can see the joint positions resulting from our experiment over time on the right side of Fig. \ref{fig:A_example}. Each motion tends to use its ``primary" joint most (the joint where the velocity is heavily scaled up) and uses the other available joints to compensate for what the primary joint cannot do. For example, Motion 1 starts out using mostly the hip, but once moving the hip no longer brings the system closer to the goal, the system uses the other joints to fold inwards and reach the goal. Ultimately, all three controllers converge on their target, but each has a different path through joint space depending on which joints we choose to emphasize in the behavior matrix $A$. The off-diagonal terms of $A$ have a more nuanced contribution; e.g. $A_{1,2}$ defines the amount that elbow velocity should be converted into hip velocity.

@@

%By learning a position-dependent joint augmentation matrix $\mathcal{A}(q)$, we are able to execute the joint behaviors discussed earlier by augment the relative velocities of our joints. \eqref{eq:A_def} constructs our overall $\mathcal{A}(q)$ as a linear combination of $A_k~\forall k\in\{1,\dots,K\}$ (each weighted by $\theta_k(q)$), where one can enforce different local joint behaviors in different regions, and compose them to create a more complex multi-behavior motion. In this paper the joint behavior matrix $\mathcal{A}(q)$ is determined using only the joint position $q$, though one could potentially use other information such as joint velocity $\dot{q}$, environment force or target task position $x^*$.\\

@@

The behavior of the JT-DS algorithm can be best understood through the lens of synergy control \cite{petrivc2013muscle}. In robotic synergy control, a robot's movements can be decomposed into a small number of synergies: principal components of the actuation-space that are sufficient to accurately recreate the desired robotic behaviors. In our case, the synergies are represented by $A_1, A_2, \dots, A_k$, and $\mathcal{A}(q)$ represents the resulting motion constructed from a superposition of different synergies (through \eqref{eq:ds}).

@@

\subsection{Estimating the Synergy Matrices}
Given the parameters of $\theta_k'(\phi(q))$ $\forall k \in \{k=1,\dots,K\}$, from \eqref{eq:A_def} one can construct $\mathcal{A}(q)$ as a linear combination of local $A_k$ matrices weighted by their scheduling parameters $\theta_k'(\phi(q))$ as follows: 
\begin{equation}
\label{eq:A}
\mathcal{A}(q) = \frac{\sum_{k=1}^K A_k \pi_k\mathcal{N}(\phi(q); \mu_k, \Sigma_k)}{\sum_{k=1}^K \pi_k\mathcal{N} (\phi(q); \mu_k, \Sigma_k)}.
\end{equation} 
Notice the resemblance of \eqref{eq:A} to the Nadaraya-Watson kernel estimator \cite{nadaraya1964regress,watson1964regress}\footnote{The Nadaraya-Watson kernel estimator is used to estimate an unknown regressive function $m(x) = \mathbb{E}\{Y|X\}$, which takes the general form of $\widehat{m}(x) = \frac{\sum_{i=1}^n y_i \mathcal{K}(x,x_i)}{\sum_{i=1}^n \mathcal{K}(x,x_i)}$ where $\mathcal{K}(x,x_i)$ is a kernel function denoting the distance or similarity of $x_i$ to the given location $x$. \cite{nadaraya1964regress,watson1964regress}} with a Gaussian pdf as its kernel function. Hence \eqref{eq:A} can be considered a type of kernel estimator, with the key distinction that the weighting functions $\theta_k'(\phi(q))$ are not determined by individual points (as in the original Nadaraya-Watson kernel estimator) but by the components of a GMM, similar to the weighting functions derived in Gaussian Mixture Regression (GMR) \cite{sung2004gmr}.

@@

One of the most important points when validating a learning from demonstration method is to evaluate the system's behavior away from demonstrations. When the current joint configuration is far from any of the local synergy regions, computing the scheduling parameters $\theta_k(\cdot)$ becomes numerically infeasible (all the Gaussians in \eqref{eq:A} $\rightarrow 0$), and so $\sum\limits_{k=1}^{K}\frac{A_k}{K}$ is used to move the robot, which is still guaranteed to move towards the target. Moreover, in overlapping local regions where multiple $A_k$'s might be in conflict, the presented system compromises between them while still stably moving to the target. The reason for this is that rather than ``determining" the velocity of the system, our $\mathcal{A}$ matrix only warps it. This means that adding multiple ``conflicting" synergies together amounts to nothing more than repeatedly warping the velocity, and still maintains the original stability property.

@@

%JTDS can be expanded to incorporate joint limits of the form $q^i_{max} > q^i > q^i_{min}$. Previous work proposed adding discontinuous limits to JT control \cite{sciavicco1988solution}, and we additionally propose a continuous modification as follows: \textcolor{red}{Remove this part? Should we not talk about continuous joint limiting?} Replace the combined synergy matrix $\mathcal{A}(q)$ with a joint-limited joint-behavior matrix $\mathcal{A}_l = S(q)\mathcal{A}(q)S^T(q)$, where $S(q)$ is a bounded positive semidefinite diagonal matrix such that  
%\begin{equation}
%\label{eq:last_criteria}
%\begin{cases}
%\begin{split}
%& s^{i}(q^i_{max}) = 0&&&\\
%& s^{i}(q^i_{min})= 0&&&
%\end{split}
%\forall i\in 1,\dots,m
%\end{cases}
%\end{equation}
%$\mathbb{A}$ is also positive semidefinite, so the system is still provably stable w.r.t. the attractor. The structure of $S$ enforces kinematic joint limits because as a joint nears one of its limits, its magnitude decreases such that it will never actually collide with the limit. One way of constructing $S$ is to use the following function:
%\begin{equation}
%s^{i}(q) =
%1 - \left ( 2\frac{q^i - q^i_{min}}{q^i_{max} - q^i_{min}} - 1 \right ) ^{4}  ~\forall i\in 1,\dots,m\\
%\end{equation}
%The algorithm can similarly be expanded to accommodate joint velocity limits by scaling the controller's velocity down such that the highest-velocity component is still within the velocity limits. Specifically, given some set of velocity constraints for each joint $i$ s.t. $\dot{q}_i < \dot{q}_{i, max}$, we can design a new joint augmentation matrix $\mathcal{A}' = r \mathcal{A}$ where $r = \min \left ( 1, \max_i \left ( \frac{\dot{q}_{i, max}}{\dot{q}_i} \right ) \right )$. This velocity scalar would slow down the joint trajectory when the robot dynamics could not execute them, but would not change the position profile of the joint motion, preserving a major aspect of the joint behavior.

@@

\section{Proving Stability of the Dynamical System}
\label{appendix:stability}
We wish to prove Proposition \ref{prop:stability}, that is, that JT-DS \eqref{eq:ds} (reproduced below)
\begin{equation*}
\dot{q} = f(q) = -\mathcal{A}(q)J^T(q)P(H(q) - x^*)
\end{equation*}
accomplishes criterion (I), where $\mathcal{A}(q)$ is positive semi-definite, and $P$ is positive definite.
\newtheorem{theorem}{Theorem}[section]
\begin{theorem}[Proof of Lyapunov Stability]
JT-DS \eqref{eq:ds} is stable in the sense of Lyapunov with respect to the Lyapunov candidate
\[ V(q) = \frac{1}{2}(H(q) - x^*)^TP(H(q) - x^*) \]
That is, 
\begin{equation}
\begin{aligned}
& 0 \prec V(q)    &
V(q^*) = 0 & \quad \forall q \neq q^*\\
%    \[\dot{V}(q) = \frac{dV}{dq}\frac{dq}{dt}(q) \preceq 0 \quad \forall q \in Q\]
\end{aligned}
\end{equation}
where $q^*$ is any joint configuration such that $H(q^*) = x^*$.
\end{theorem}
The first two statements are trivially true because $P$ is positive definite and the rest of $V$ is a square that is only $0$ when $H(q) = x^*$. To prove the last statement, we find $\frac{dV}{dt}$:
\begin{equation}
\begin{aligned}
\frac{dV(q)}{dt} &= (H(q) - x^*)^TPJ(q)\dot{q}\\
&= -(H(q) - x^*)^TPJ(q)\mathcal{A}(q)J^T(q)P(H(q) - x^*)\\
&= -(H(q) - x^*)^TPJ(q)\sum_{k=1}^{K}\underbrace{\theta_k(q)}_{0\leq}\underbrace{A_k}_{0\preceq}\\&~~~~~~ \cdot J^T(q)P(H(q) - x^*) \leq 0
\end{aligned}
\end{equation}
By observation, each and every term in the final expression is multiplied by its transpose (creating a square) except for $\mathcal{A}(q)$, which is positive semi-definite. This means that the expression is guaranteed to be negative semi-definite. Therefore, JT-DS \eqref{eq:ds} is globally Lyapunov stable; i.e. $ \| H(q)-x^*\| $ and $ \dot{q} $ are bounded.
